Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-19 thesis/chapters/ch_introduction.tex
Finalized proof read of introduction. First draft of intro complete. Updating and adding references.

In galaxy-scale hydrodynamics, the costs in resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model. Stars form from fluid elements that surpass a variety of threshold conditions at an assumed rate and efficiency. Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion. Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
%cite?,
or that gas meet a minimum \Hmolecular mass fraction \citep[e.g.][]{Kuhlen2012}
%\citep[e.g.][]{}
. Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars. Briefly, some form of the following equation is usually adopted to describe the star formation rate density ($\dot{\rho}_{\rm SF}$),
\begin{equation}
\label{intro:eq:sfr}
 \dot{\rho}_{\rm SF} = \epsilon \frac{\rho_{\rm gas}}{t_*},
\end{equation}
, where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
\begin{equation}
  t_* = t_{\rm ff} = \sqrt{\frac{3\pi}{32 \rm{G} \rho_{\rm gas}}}.
\end{equation}
In many cases, $\epsilon$ is fixed to some small value ($\sim$ 0.01) \citep{KrumholzTan2007} meant to represent a galaxy-scale average of star formation efficiency, even though this may vary significantly between individual molecular clouds \citep{Grudic2018}. High-resolution simulations, where the mass of stars that would form in a single time step ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.

Recent work has demonstrated that variations in these implementations can lead to dramatic differences in the outcome of the simulated galaxies \citep[e.g.][]{Hopkins2013,Munshi2018}. However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$).

@@

Stars, particularly large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment. As demonstrated in \cite{Revaz2016}, this approach is reasonable so long as the mass of the star particle is large enough to fully sample the IMF ($> 10^{4}$~M$_{\odot}$). In high resolution simulations, particularly simulations of small, low-mass systems like dwarf galaxies, this is no longer the case. This leads to inconsistencies in both the effective metal yield of the modelled stars, and (often) an artificial reduction of the effects of stellar feedback. Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{MUGS2010,FIRE,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}. However, each of these methods utilizes a sub-grid recipe in some fashion to improve upon the SSPs. On the other extreme are highly resolved simulations which model star formation with ``sink particles" \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback. These recipes are often computationally expensive, however, restricting their use over long timescales (100's to 1000's of Myr or more) in galaxy-scale simulations.

In this \dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF. This allows us to place unprecidented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.

@@

The first models of galacitc evolution produced galaxies with stellar masses far in excess of what is observed in the Universe, converting a substantial fraction of their baryons into stars. From these initial works, it was clear that some form of feedback process must take place to self-regulate star formation within galaxies. With observations of metal abundances in the CGM around galaxies \citep[see][ for a recent review]{Tumlinson2017}, and of fast-moving outflows from star forming galxaies \citep[see][ for a review]{Veilleux2005}, it was additionally clear that some mechanism must exist to drive these outflows. Stellar feedback became the clear physical mechanism to account for both of these phenomena.\footnote{Except maybe for more massive galaxies, where active galactic nuclei likely plan some role in regulating star formation and certainly play a role in driving outflows \citep[e.g.][]{Fabian2012}.}

Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:supernovae}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution). Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties, and includes stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).

Although not included in this \dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution. A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references). In brief, cosmic rays can be a dominant source of heading in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}. In addition, binarity is often ignored in models of stellar feedback, but can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations, typically increasing their total energy output and decreasing the typical ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}). Finally, exoctic sources of stellar feedback, such as hupernovae, high-mass X-ray binaries, and neutron star neutron star mergers can also be a potentially important source of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}. However, the uncertainties in the frequency and delay time distributions for when these events should occur, and there relative rarity preclude including these effects in this \dissertation.

@@

In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion. In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case. The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events. This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lesssim 10^5$~K, as opposed to $T > 10^7$~K, or so). This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy. This is still a problem today in large-box simulations of cosmological volumes which have insufficient resulution to resolve individual SNe. While some of the initial, ad-hoc fixes for this problem (e.g. turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{FIRE,Simpson2015,Hopkins2018}.

High resolution simulations, like those developed in this \dissertation, can typically resort to utilizing pure thermal energy injection into the fluid elements surrounding the supernova site and avoiding artificial ``overcooling". This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}. However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective. In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}. Including these physics, as discussed below, greatly reduces the typical ISM densities in which SNe occur, greatly increasing the likelihood that these events are well resolved.

@@

We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter1} and \ref{ch:chapter2}. In brief, \cite{Leitherer1999}, \cite{Agertz2013}, and others demonstrated that stellar radiation, accounts for a substantial fraction of the total energy output of a stellar population. Ionizing photons from young, massive stars can photoionize and photoheat the gas surrounding sites of recent star formation. This effectively pre-processes the local environment within which SNe occur, often increasing the effectiveness of SNe in regulating star formation and driving outflows \citep{Hu2016}. In addition, radiation pressure in the single-scattering limit (from UV photons) and rescattered infrared photons has been used as an additional source of pre-SN feedback \citep[e.g.][]{FIRE}. However, due in part to differences in how ionizing radition is followed across simulations, there is disagreement as to exactly how and in what conditions this acts as a source of feedback (see \cite{Krumholz2018} for a detailed examination of this problem).

Non-ionizing radiation also contributes to the regulation of star formation and the multi-phase ISM. Far ultraviolet (FUV) photons contribute to gas heating via the photoelectric heating of dust grains. This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}. Lyman-Werner (LW) band radiation regulates the \Hmolecular abundance, which is particularly important in low-metallicity environments where \Hmolecular is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.

@@

Stellar winds, in addition to stellar radiation, are a potentially important source of pre-SN feedback that helps regulate star formation in / around the birth clouds of newly formed stars. However, the hot ($T>10^{6}$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) winds from massive stars \citep{Weaver1977} are challenging to model self-consistently in galaxy-scale simulations. For this reason, there has been comparatively little research on how they affect global galaxy properties, even though some models do include their energy injection in an integrated / approximate fashion \citep[e.g.][]{FIRE}. However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment. For these reasons we include stellar wind feedback in this disseration, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored. It is thus likely subdominant to radiation feedback.}

@@

The Milky Way and its local environment is host to a diverse collection of dwarf galaxies. The properties of these galaxies have been nicely summarized in a recent review \citep{Tolstoy2009}, and again in \cite{McConnachie2012}. However, the number of known Local Group dwarf galaxies has increased dramatically since that time, particularly for the Milky Way, whose known satellite population has more than doubled. This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint galaxies (UFDs, \cite{Willman2005}).\footnote{See \cite{Simon2019} for a recent review}. The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope producing an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.

While there is no real sharp transition where a galaxy is considered a ``dwarf" galaxy, historical definitions are based on luminosity, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale. \cite{Bullock2017} suggests a deliniation based on stellar mass. For this \dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs. In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$, \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback (cite).

@@

The first studies of stellar abundances in the Local Group focused on stars in nearby dSph's, and massive stars in the LMC, SMC, and similar, more massive dwarf galaxies \citep[e.g.][]{}. These studies typically obtained abundances for only a small sample ($\sim$ 10) stars, limiting the extent to which they can be used to test models of galacitc chemical evolution.  However, the advent of high-resolution spectrographs at both Keck and the Very Large Telescope -- capable of obtaining the spectra of many stars with a single pointing -- have dramatically increased the sample size of stellar abundances in nearby dwarf galaxies \citep[e.g.][]{}.

Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references). Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above 100 \citep{Muratov2015,Christensen2018}. Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies. \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy. However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback. However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals (see Section~\ref{intro:sec:Leo P}). This is significant evidence for metal-enriched, feedback-driven galactic winds operating in these low mass dwarf galaxies.

Finally, the low metallicities of the lowest mass dwarf galaxies make them ideal places to better constrain large uncertainties in stellar nucleosynthesis \citep{FrebelNorris2015,Frebel2018}. At these low metallicities, the number of possible enrichment events that could have possibly contributed to the observed stellar abundances decreases significantly, increasing the possibility of using these abundance patterns to constrain the yields of individual sources. This is particularly true for exotic enrichment events, like those expected to be significant sources of r-process elements, which are potentially so rare that only one or fewer events would be expected in an individual low-mass galaxy.

The most prominant example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS origin for the enrichment. This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to this conclusion \citep[e.g.][]{Siegel2018}. Interestingly, the lack of these extreme r-process abundances in other UFDs suggests that another source of r-process must exist \citep{Ji2016b}. Some of the significant uncertainties in interpreting these observations lie with understanding how r-process elements mix within the ISM and are ejected from low mass dwarf galaxies. Recent research has examined how metals from individual enrichement events may mix and evolve in a variety of contexts \citep[e.g.][]{Bland-Hawthorn2015,Ritter2015,Montes2016,Safarzadeh2017}, but there is still much to be understood about this process. In particular, there is still much to be gained from adapting insights from these types of simulations to the modelling used to interpret observations of stellar abundances (as discussed in more detail in Section~\ref{intro:sec:onezone}).

@@

\begin{figure}
 \centering
 \includegraphics[width=0.975\linewidth]{figures/intro/Leo_P}
 \caption{The Leo P dwarf galaxy. \textbf{Left:} \hi contours from the VLA at 32'' resolution (the lowest resolution available) overlaid on top of an optical LBT image. This image is adopted from the top-left panel of Figure 4 in \cite{Bernstein-Cooper2014}. \textbf{Right:} H$\alpha$ emission (contours) overlaid on top of an HST optical image. The \hii region analyzed in \cite{McQuinn2015} to obtain gas-phase metallicities is the blue clump of H$\alpha$ at the bottom of the image. This image is adopted from Figure 10 of \cite{Evans2019}. \textit{Note:} the veritcal axes are inverted between the left and right panels.}
 \label{intro:fig:Leo P}
\end{figure}

>>>>

In galaxy-scale hydrodynamics, the costs in resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model. Stars form from fluid elements that surpass a variety of threshold conditions at an assumed rate and efficiency. Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion. Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \cdot \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
%cite?,
or that gas meet a minimum \Hmolecular mass fraction \citep[e.g.][]{Kuhlen2012}
%\citep[e.g.][]{}
. Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars. Briefly, some form of the following equation is usually adopted to describe the star formation rate density,
\begin{equation}
\label{intro:eq:sfr}
 \dot{\rho}_{\rm SF} = \epsilon \frac{\rho_{\rm gas}}{t_*},
\end{equation}
where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
\begin{equation}
  t_* = t_{\rm ff} = \sqrt{\frac{3\pi}{32 \rm{G} \rho_{\rm gas}}}.
\end{equation}
In many cases, $\epsilon$ is fixed to some small value ($\sim$ 0.01) \citep{KrumholzTan2007} meant to represent a galaxy-scale average of star formation efficiency, even though this may vary significantly between individual molecular clouds \citep{Grudic2018}. High-resolution simulations, where the mass of stars that would form in a single time step ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.

Recent work has demonstrated that variations in these implementations can lead to dramatic differences in the outcome of the simulated galaxies \citep[e.g.][]{Hopkins2013,Munshi2018}. However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$) \citep{Orr2018,FIRE2}.

@@

Stars, particularly in large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment. As demonstrated in \cite{Revaz2016}, this approach is reasonable so long as the mass of the star particle is large enough to fully sample the IMF ($> 10^{4}$~M$_{\odot}$). In high resolution simulations, particularly simulations of small, low-mass systems like dwarf galaxies, this is no longer the case. This leads to inconsistencies in both the effective metal yield of the modeled stars, and (often) an artificial reduction of the effects of stellar feedback. Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{MUGS2010,FIRE,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}. However, each of these methods utilizes a sub-grid recipe in some fashion to improve upon the SSPs. On the other extreme are highly resolved simulations which model star formation with ``sink particles" \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback. These recipes are often computationally expensive, however, restricting their use over long timescales (100's to 1000's of Myr or more) in galaxy-scale simulations.

In this \dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF. This allows us to place unprecedented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.

@@

The first models of galactic evolution produced galaxies with stellar masses far in excess of what is observed in the Universe.
%, converting a substantial fraction of their baryons into stars.
From these initial works, it was clear that some form of feedback process must take place to self-regulate star formation within galaxies. With observations of metal abundances in the CGM around galaxies \citep[see][ for a recent review]{Tumlinson2017}, and of fast-moving outflows from star forming galaxies \citep[see][ for a review]{Veilleux2005}, it was additionally clear that some mechanism must exist to drive these outflows. Stellar feedback became the clear physical mechanism to account for both of these phenomena.\footnote{Except maybe for more massive galaxies, where active galactic nuclei may play some role in regulating star formation and certainly play a role in driving outflows \citep[e.g.][]{Fabian2012}. We do not discuss this source of feedback further in this \dissertation aside from noting that it is another significant uncertainty in our understanding of galactic evolution.}

Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:supernovae}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution). Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties. This includes both stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).

Although not included in this \dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution. A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references). In brief, cosmic rays can be a dominant source of heating in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}. Binarity is often ignored in models of stellar feedback. The effects of binary evolution can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations. Typically, this increases their total energy output and decreases the ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}). Finally, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}. However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \dissertation.

@@

In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion. In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case. The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events. This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lesssim 10^5$~K, as opposed to $T > 10^7$~K, or so). This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before it has time to make a significant dynamical impact of the galaxy. This is still a problem today in large-box simulations of cosmological volumes which have insufficient resolution to resolve individual SNe. While some of the initial, ad-hoc fixes for this problem (e.g. turning off cooling for some time in SN affected fluid elements or decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{FIRE,Simpson2015,Hopkins2018}.

High resolution simulations, like those developed in this \dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}. However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective. In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}. Including these physics, as discussed below, greatly reduces the typical ISM densities in which SNe occur, greatly increasing the likelihood that these events are well resolved.

@@

We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter1} and \ref{ch:chapter2}. In brief, \cite{Leitherer1999}, \cite{Agertz2013}, and others have demonstrated that stellar radiation accounts for a substantial fraction of the total energy output of a stellar population. Ionizing photons from young, massive stars can photoionize and heat the gas surrounding sites of recent star formation. This pre-processes the local environment within which SNe occur, often increasing the effectiveness of SNe in regulating star formation and driving outflows \citep{Hu2016}. In addition, radiation pressure in the single-scattering limit (from UV photons) and rescattered infrared photons has been used as an additional source of pre-SN feedback \citep[e.g.][]{FIRE}. However, due in part to differences in how ionizing radiation is followed across simulations, there is disagreement as to exactly how and in what conditions this acts as a source of feedback (see \cite{Krumholz2018} for a detailed examination of this problem).

Non-ionizing radiation also contributes to the regulation of star formation and the multi-phase ISM. Far ultraviolet (FUV) photons contribute to gas heating via the photoelectric heating of dust grains. This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}. Lyman-Werner (LW) band radiation regulates the \Hmolecular~ abundance, which is particularly important in low-metallicity environments where \Hmolecular~ is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.

The simplest way to model stellar radiation feedback is to apply an optically thin, analytic radiation profile, such as the galaxy-centered exponential photoelectric heating profile used in \cite{Tasker2009}, or $1/r^2$ profiles from individual sources \citep[e.g.][]{Forbes2016}. However, radiative transfer effects, such as gas self-shielding, are often important, particularly for ionizing radiation. Solving the equations of radiative transfer directly in simulations -- as is done with ray tracing methods -- is computationally expensive and scales significantly with the number of sources. For this reason, approximate methods, such as flux-limited diffusion, treat radiation as a fluid, removing the scaling of computational cost with the number of sources. In this \dissertation, we follow the evolution of galaxies that have at most $10 - 100$ ionizing sources at one time, making it computationally feasible to use the accurate adaptive ray-tracing radiative transfer method implemented in \code{Enzo}.

@@

Stellar winds, in addition to stellar radiation, are a potentially important source of pre-SN feedback that helps regulate star formation in / around the birth clouds of newly formed stars. However, the hot ($T>10^{6}$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) winds from massive stars \citep{Weaver1977} are challenging to model self-consistently in galaxy-scale simulations. For this reason, there has been comparatively little research on how they affect global galaxy properties, even though some models do include their energy injection in an integrated / approximate fashion \citep[e.g.][]{FIRE}. However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment. For this reason we include stellar wind feedback in this \dissertation, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in simulations where radiation feedback is ignored. It is thus likely sub-dominant to radiation feedback.}

@@

The Milky Way and its local environment is host to a diverse collection of dwarf galaxies. The properties of these galaxies have been nicely summarized in a recent review \citep{Tolstoy2009}, and again in \cite{McConnachie2012}. However, the number of known Local Group dwarf galaxies has increased dramatically since that time, particularly for the Milky Way, whose known satellite population has more than doubled. This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint dwarf galaxies (UFDs, \cite{Willman2005}).\footnote{See \cite{Simon2019} for a recent review}. The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope expected to produce an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.

While there is no true sharp transition below which a galaxy is considered ``dwarf", historical definitions are based on luminosity cuts, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale. \cite{Bullock2017} suggests a delineation based on stellar mass. For this \dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs. In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$ \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies
% need citations
, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback
% need citations
.

@@

The first studies of stellar abundances in the Local Group focused on stars in nearby dwarf spheroidals (dSph's), and massive stars in the LMC, SMC, and similar, more massive dwarf galaxies. These studies typically obtained abundances for only a small sample ($\sim$ 10) stars, limiting the extent to which they can be used to test models of galactic chemical evolution.  However, the advent of high-resolution spectrographs at both Keck and the Very Large Telescope -- capable of obtaining the spectra of many stars with a single pointing -- have dramatically increased the sample size of stellar abundances in nearby dwarf galaxies.

Stellar feedback drives outflows, galactic winds, from galaxies across all scales
%(references).
Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above 100 \citep{Muratov2015,Christensen2018}. Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies. \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy. However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (primarily ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback. However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals (see Section~\ref{intro:sec:Leo P}). This is significant evidence for metal-enriched, feedback-driven galactic winds operating in these low mass dwarf galaxies.

Finally, the low metallicities of the lowest mass dwarf galaxies make them ideal places to better constrain large uncertainties in stellar nucleosynthesis \citep{FrebelNorris2015,Frebel2018}. At these low metallicities, the number of possible enrichment events that could have possibly contributed to the observed stellar abundances decreases significantly, increasing the possibility of using these abundance patterns to constrain the yields of individual sources. This is particularly true for exotic enrichment events, like those expected to be sources of r-process elements, which are potentially so rare that only one or fewer events would be expected in an individual low-mass galaxy.

The most prominent example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS of r-process enrichment. This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to the dominant source of r-process enrichment \citep[e.g.][]{Siegel2018}. Interestingly, the lack of these extreme r-process abundances in other UFDs suggests that another source of r-process must exist \citep{Ji2016b}. Some of the significant uncertainties in interpreting these observations lie with understanding how r-process elements mix within the ISM and are ejected from low mass dwarf galaxies. Recent research has examined how metals from individual enrichment events may mix and evolve in a variety of contexts \citep[e.g.][]{Bland-Hawthorn2015,Ritter2015,Montes2016,Safarzadeh2017}, but there is still much to be understood about this process. In particular, there is still much to be gained from adapting insights from these types of simulations to the modeling used to interpret observations of stellar abundances (as discussed in more detail in Section~\ref{intro:sec:onezone}).

@@

\begin{figure}
 \centering
 \includegraphics[width=0.975\linewidth]{figures/intro/Leo_P}
 \caption{The Leo P dwarf galaxy. \textbf{Left:} \hi contours from the Very Large Array (VLA) at 32'' resolution overlaid on top of an optical Large Binocular Telescope image. 32'' is the lowest resolution \hi observation available of Leo P from the VLA, which best traces diffuse, warm ($T \sim 10^3$~K) \hi in the galaxy and exhibits the full spatial extent of its gas content. This image is adopted from the top-left panel of Figure 4 in \cite{Bernstein-Cooper2014}. \textbf{Right:} H$\alpha$ emission (contours) overlaid on top of a Hubble Space Telescope (HST) optical image. The \hii region analyzed in \cite{McQuinn2015} to obtain gas-phase metallicities is the blue clump of H$\alpha$ towards the bottom of the image. This image is adopted from Figure 10 of \cite{Evans2019}. Note the inversion in the vertical axes between the left and right panels.}
 \label{intro:fig:Leo P}
\end{figure}
